Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-06-18 Manuscript/manuscriptPS.tex

\begin{figure}[!tb]
  \centering
  \includegraphics[width=8.5cm]{../Figs/fig1_POPS.pdf}
  \caption{\label{PShgSIGNSsimpson}
    The headgroup and glycerol backbone region of the (A) Refocused-INEPT spectrum and
    (B) 2D R-PDLF spectra.
    (C) Experimental S-DROSS data (points), and SIMPSON simulations (blue lines) with
    the C--H bond order parameter values of $-0.12$ for the $\beta$-carbon, and $+0.09$ and $-0.02$
    for the $\alpha$-carbon.
    Dashed gray line is the S-DROSS curve from a SIMPSON simulation with a positive value ($+0.02$) 
    for the smaller $\alpha$-carbon C--H bond order parameter.
  }
\end{figure}
\begin{figure}[!htb]
  \centering
  \includegraphics[width=9.0cm]{../Figs/PCPScomp.eps}
  \caption{\label{HGorderParameters}
    (A) Chemical structures and labels for the headgroup and glycerol backbone carbons.
    (B) Headgroup and glycerol backbone order parameters of POPS (T = 298 K) measured in this work compared
    with the previously published values from DOPS ($T=303$~K, $^2$H NMR, 0.1~M of NaCl) \cite{browning80} and 
    POPC  ($T=300$~K, $^{13}$C NMR) \cite{ferreira13} experiments. Signs of the PS order parameters
    are measured in this work whereas signs of the PC order parameters are measured previously~\cite{ferreira16}.
    The size of errorbars ($\pm$0.02) shown for $^{13}$C NMR data is justified previously~\cite{botan15,ollila16}. 
  }
  \todo{Replacing the "literature" with "from Ref X" has been suggested  https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/34.
  We can do this just before submission when citation numbers will not change anymore.}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/structures.eps}
  \caption{\label{HGstructuresPSandPC}
    Overlayed snapshots from simulations conducted with CHARMM36---the force field producing the best agreement with experiments---demonstrate the conformational fluctuations around
    (A) C$_\alpha$-C$_\beta$-C$_\gamma$-O$_\gamma$ and  O$_\alpha$-C$_\alpha$-C$_\beta$-N dihedrals
    of the PS headgroup and (B) N-C$_\beta$-C$_\alpha$-O$_\alpha$ and C$_\beta$-C$_\alpha$-O$_\alpha$-P
    dihedrals of the PS and PC headgroups. The trajectory used for CHARMM36 POPC is available at Ref.~\citenum{POPCcharmm36T303K}.}
{ \todo{TMF: I find these pictures very interesting but at the same time a bit difficult to follow and I am not sure if i get them right. In each picture two dihedrals distributions are depicted right? so there are two pictures superimposed as far as I understand. Maybe this could be shortly explained in the caption or using a link to the methods section?}}

\end{figure}

@@

\listoftodos

>>>>

\begin{figure}[!tb]
  \centering
  \includegraphics[width=8.5cm]{../Figs/fig1_POPS.pdf}
  \caption{\label{PShgSIGNSsimpson}
    The headgroup and glycerol backbone region of the (A) Refocused-INEPT spectrum and
    (B) 2D R-PDLF spectra.
    (C) Experimental S-DROSS data (points), and SIMPSON simulations (blue lines) with
    the C--H bond order parameter values of $-0.12$ for the $\beta$-carbon, and $+0.09$ and $-0.02$
    for the $\alpha$-carbon.
    Dashed gray line is the S-DROSS curve from a SIMPSON simulation with a positive value ($+0.02$) 
    for the smaller $\alpha$-carbon C--H bond order parameter.
  }
\end{figure}
\begin{figure}[!htb]
  \centering
  \includegraphics[width=9.0cm]{../Figs/PCPScomp.eps}
  \caption{\label{HGorderParameters}
    (A) Chemical structures and labels for the headgroup and glycerol backbone carbons.
    (B) Headgroup and glycerol backbone order parameters of POPS (T = 298 K) measured in this work compared
    with the previously published values from DOPS ($T=303$~K, $^2$H NMR, 0.1~M of NaCl) \cite{browning80} and 
    POPC  ($T=300$~K, $^{13}$C NMR) \cite{ferreira13} experiments. Signs of the PS order parameters
    are measured in this work whereas signs of the PC order parameters are measured previously~\cite{ferreira16}.
    The size of errorbars ($\pm$0.02) shown for $^{13}$C NMR data is justified previously~\cite{botan15,ollila16}. 
  }
  %\todo{Replacing the "literature" with "from Ref X" has been suggested  https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/34.
  %We can do this just before submission when citation numbers will not change anymore.}
  %SAMULI: Maybe better to do in revision stage because citations might still change.
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/structures.eps}
  \caption{\label{HGstructuresPSandPC}
    Overlayed snapshots from simulations conducted with CHARMM36---the force field producing the best agreement with experiments---demonstrate the conformational fluctuations
    of lipid headgroups.
    (A) Overlaying  C$_\gamma$-C$_\beta$-C$_\alpha$ carbons demonstrate fluctuations around O$_\gamma$-C$_\gamma$-C$_\beta$-C$_\alpha$, C$_\gamma$-C$_\beta$-C$_\alpha$-O$_\alpha$,
    and N-C$_\beta$-C$_\alpha$-O$_\alpha$ dihedrals of the PS headgroup and
    (B) overlaying C$_\beta$-C$_\alpha$-O$_\alpha$ carbonds demonstrate fluctuations around N-C$_\beta$-C$_\alpha$-O$_\alpha$ and C$_\beta$-C$_\alpha$-O$_\alpha$-P
    dihedrals of the PS and PC headgroups. The trajectory used for CHARMM36 POPC is available at Ref.~\citenum{POPCcharmm36T303K}.}
  %{ \todo{TMF: I find these pictures very interesting but at the same time a bit difficult to follow and I am not sure if i get them right. In each picture two dihedrals distributions are depicted right? so there are two pictures superimposed as far as I understand. Maybe this could be shortly explained in the caption or using a link to the methods section?}} 
  %SAMULI: I have now updated the caption to contain information about the atoms used in the overlay. Hopefully it is more clear now? 
\end{figure}

@@

%\listoftodos
